Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
British-isation except for section 3

% !TeX root = ../main-paper.tex
\begin{figure}[!h]
    \centering
    \includegraphics[width=.9\textwidth]{figs/overview-intro.pdf}
    \caption{%
    Overview of the pipeline under study.
    From previously-extracted images of directory entries, 
    we perform OCR and named entity recognition (NER) using different techniques.
    We aim at answering the following questions:
    \emph{How noisy are modern, out-of-the-box OCR systems?}
    \emph{What is the behavior of NER when OCR is noisy?}
    \emph{Can NER be made more robust to OCR noise?}
    }
    \label{<label>}
\end{figure}
\clearpage% force float flush!

@@

% General context + scope limitation
OCRed texts are generally not sufficient to build a high level, semantic view of a collection of historical documents.
A subsequent stage is often needed to extract the pieces of information most likely to be searched for by users, such as named entities: people, organizations, dates, places, etc.
Indeed, being able to properly tag text tokens unlocks the ability to relate entities, and provide colleagues from other fields with databases ready for exploitation.

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due multiple causes related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts, and also from the errors introduced into the text by the OCR step.

In this article, we focus on a peculiar category of historical printed books: city trade directories of Paris from the XIX\textsuperscript{th} century (1801 - 1854).
They contain hundred-pages long lists of people, along with their activity and their address, and provide valuable fine-grained knowledge to study the social dynamics of the city over time.
Despite containing roughly the same information, the diversity in layouts, information organization and digitizing quality is challenging both for OCR and NER.

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.

>>>>

% !TeX root = ../main-paper.tex
\begin{figure}[!h]
    \centering
    \includegraphics[width=.9\textwidth]{figs/overview-intro.pdf}
    \caption{%
    Overview of the pipeline under study.
    From previously-extracted images of directory entries, 
    we perform OCR and named entity recognition (NER) using different techniques.
    We aim at answering the following questions:
    \emph{How noisy are modern, out-of-the-box OCR systems?}
    \emph{What is the behaviour of NER when OCR is noisy?}
    \emph{Can NER be made more robust to OCR noise?}
    }
    \label{<label>}
\end{figure}
\clearpage% force float flush!

@@

% General context + scope limitation
OCRed texts are generally not sufficient to build a high level, semantic view of a collection of historical documents.
A subsequent stage is often needed to extract the pieces of information most likely to be searched for by users, such as named entities: people, organisations, dates, places, etc.
Indeed, being able to properly tag text tokens unlocks the ability to relate entities, and provide colleagues from other fields with databases ready for exploitation.

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artefacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts, and also from the errors introduced into the text by the OCR step.

In this article, we focus on a peculiar category of historical printed books: city trade directories of Paris from the XIX\textsuperscript{th} century (1801 - 1854).
They contain hundred-pages long lists of people, along with their activity and their address, and provide valuable fine-grained knowledge to study the social dynamics of the city over time.
Despite containing roughly the same information, the diversity in layouts, information organisation and digitising quality is challenging both for OCR and NER.

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognises business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.

### 2022-01-20 src-latex/parts/20-related-work.tex
Section 6
British-isation except for section 3

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of the text that match patterns like in \cite{bell2020automated,nouvel2011} or dictionary (gazetteers, author lists, etc.) entries like in \cite{mansouri2008,maurel2011}.
Such kind of approaches achieve very good results when applied to a specialized domain corpus and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances as shown in the recent survey proposed by \cite{li2020}. This survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data. This strategy has been adopted by \cite{Labusch2020NamedED} to extract named entities in OCRed historical texts in German, French, and English. However, the NER performance drops significantly as the quality of the OCR decreases and is correlated with its decrease.

Several recent studies have focused on the impact of OCR quality on NER results. Most of the time, they have evaluated NER approaches based on deep learning architectures as they seem to adapt more easily to OCR errors than rule-based or more classical supervised approaches.
\cite{van2020assessing} use the English model \textit{en-core-web-lg} provided by SpaCy\footnote{\url{https://spacy.io/}} library to perform NER on a corpus made of many journal articles with different levels of OCR errors.
For each OCRed article, a ground truth text is available so that the Word Error Rate (WER) can be computed.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F1-score for each NER class and each article, i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four supervised NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on CoNLL-02 and CoNLL-03 NER benchmark corpora, degraded by applying four different types of OCR noise. Overall, NER F-measure drops from 90\% to 50\% when the Word Error Rate increases from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors. 
Two approaches have been proposed by \cite{huynh2020use} and \cite{marz2021data}  to reduce the negative impact of OCR errors on NER performance on historical texts.
The former applies a spelling correction tool to several corpora with variable OCR error rates. 
As long as OCR errors remain low ($CER<2\%$ and $WER<10\%$), this strategy makes it possible to maintain good NER results. However, the F1-score starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalization of an off-the-shelf NER model from modern texts to historical texts.
Finally, reusing a model trained on clean modern data, including embeddings computed on a historical corpus, and fine-tuned on a noisy historical ground truth has proven to be the most effective strategy.

@@

@@

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (jan. 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a weel-known French language model derived from BERT, of which there are already trained versions for the NER task on the Hugging Face library.

>>>>

Many approaches have been designed to recognise named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of the text that match patterns like in \cite{bell2020automated,nouvel2011} or dictionary (gazetteers, author lists, etc.) entries like in \cite{mansouri2008,maurel2011}.
Such kind of approaches achieve very good results when applied to a specialised domain corpus and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances as shown in the recent survey proposed by \cite{li2020}. This survey concludes that fine-tuning general-purpose contextualised language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data. This strategy has been adopted by \cite{Labusch2020NamedED} to extract named entities in OCRed historical texts in German, French, and English. However, the NER performance drops significantly as the quality of the OCR decreases and is correlated with its decrease.

Several recent studies have focused on the impact of OCR quality on NER results. Most of the time, they have evaluated NER approaches based on deep learning architectures as they seem to adapt more easily to OCR errors than rule-based or more classical supervised approaches.
\cite{van2020assessing} use the English model \textit{en-core-web-lg} provided by SpaCy\footnote{\url{https://spacy.io/}} library to perform NER on a corpus made of many journal articles with different levels of OCR errors.
For each OCRed article, a ground truth text is available so that the Word Error Rate (WER) can be computed.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F1-score for each NER class and each article, i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four supervised NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on CoNLL-02 and CoNLL-03 NER benchmark corpora, degraded by applying four different types of OCR noise. Overall, NER F-measure drops from 90\% to 50\% when the Word Error Rate increases from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors. 
Two approaches have been proposed by \cite{huynh2020use} and \cite{marz2021data}  to reduce the negative impact of OCR errors on NER performance on historical texts.
The former applies a spelling correction tool to several corpora with variable OCR error rates. 
As long as OCR errors remain low ($CER<2\%$ and $WER<10\%$), this strategy makes it possible to maintain good NER results. However, the F1-score starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalisation of an off-the-shelf NER model from modern texts to historical texts.
Finally, reusing a model trained on clean modern data, including embeddings computed on a historical corpus, and fine-tuned on a noisy historical ground truth has proven to be the most effective strategy.

@@

\nathalie{A compléter ici?}

@@

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (as of january 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi layer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pre-trained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a well-known French language model derived from BERT, of which there are already trained versions for the NER task on the Hugging Face library.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Updates from Overleaf
British-isation except for section 3

\subsection{Results and discussion}
Table \ref{tab:experiment-1-models-performances} and Figure \ref{fig:f1-vs-trainsize} display the averaged precision, recall and F1-score for all models on the 8 subsets of ground-truth examples.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

It appears that pretraining the CamemBERT model on OCR texts seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from the pretraining are specialized on noisy texts and therefore less adapted to clean texts.
The pretraining aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counter-productive when the texts do not contain these types of errors.

\begin{table}[h!]
\centering
\caption{\label{tab:experiment-1-models-performances} F1 score, precision and recall measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes.}
\begin{tabular}{llrrrrrrrr}
       & Training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & CmBERT &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & CmBERT-ptrn &  \textbf{92.2} &  \textbf{92.9} &  \textbf{93.6} &  \textbf{93.8} &  93.8 &  94.1 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & CmBERT &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & CmBERT-ptrn &  90.8 &  91.8 &  92.9 &  93.0 &  93.0 &  93.4 &  94.1 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & CmBERT &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & CmBERT-ptrn &  93.6 &  94.0 &  94.4 &  94.6 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\end{table}

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Graph view of the metrics displayed in~\cref{tab:experiment-1-models-performances}. As SpaCy NER is outperformed by both BERT models from the start, CmBERT slightly surpasses the pre-trained version when the number of training examples becomes large.}.
\end{figure}

>>>>

\subsection{Results and discussion}
Table \ref{tab:experiment-1-models-performances} and Figure \ref{fig:f1-vs-trainsize} display the averaged precision, recall and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

It appears that pre-training the CamemBERT model on OCR texts seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from the pret-raining are specialised on noisy texts and therefore less adapted to clean texts.
The pre-training aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counter-productive when the texts do not contain these types of errors.

\begin{table}[ht!]
\centering
\caption{\label{tab:experiment-1-models-performances} F1 score, precision and recall measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes.}
\begin{tabular}{llrrrrrrrr}
       & Training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & CmBERT &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & CmBERT-ptrn &  \textbf{92.2} &  \textbf{92.9} &  \textbf{93.6} &  \textbf{93.8} &  93.8 &  94.1 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & CmBERT &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & CmBERT-ptrn &  90.8 &  91.8 &  92.9 &  93.0 &  93.0 &  93.4 &  94.1 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & CmBERT &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & CmBERT-ptrn &  93.6 &  94.0 &  94.4 &  94.6 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\end{table}

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Graph view of the metrics displayed in~\cref{tab:experiment-1-models-performances}. As SpaCy NER is outperformed by both BERT models from the start, CmBERT slightly surpasses the pre-trained version when the number of training examples becomes large.}.
\end{figure}

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
British-isation except for section 3

We leverage the labeled datasets NER-reference, NER-pero and NER-tesseract created as explained in \cref{sec:dataset}.
Kraken is left aside as it produces poor results that would require removing 500 entries from all datasets to keep the same set of valid entries.

@@

CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-reference and NER-pero.
Finally the metrics are measured against the three tests sets.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{reference}$).  Results show that best performances on noisy entries are obtained when the model has been pre-trained and fine-tuned for NER on examples affected with a similar OCR noise.}
\end{figure}

>>>>

We leverage the labeled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Kraken is left aside as it produces poor results that would require removing 500 entries from all datasets to keep the same set of valid entries.

@@

CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
Finally the metrics are measured against the three tests sets.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).  Results show that best performances on noisy entries are obtained when the model has been pre-trained and fine-tuned for NER on examples affected with a similar OCR noise.}
\end{figure}
